Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-04-28 paper/ms.tex
Add plotting details section

>>>>

\noindent
{\bf Plotting Details}
\\
\noindent
We saved snapshots in intervals of $0.005$ in the time units of the
simulation, $\textrm{kpc}/(\textrm{km}/\textrm{s})$, which is very nearly
equal to $1\,\textrm{Gyr}$ (it is $\sim0.977\,\textrm{Gyr}$). Therefore,
throughout this work we referred to the native code time unit as
$\textrm{Gyr}$. None of our results are sensitive to this choice.

In order to remove numerical noise in several quantities we computed, we
applied a Savitzky-Golay filter\cite{1964AnaCh..36.1627S} as implemented in
\texttt{scipy} using a window length of $81$ and polynomial order of $3$. This
filter was applied to plots of pattern speeds, bar lengths and strengths,
torques, and angle differences.
